Research?

### 2014-04-09 final_presentation/presentation.tex
Wrote for the presentation.

\usetheme{Dresden}
\usecolortheme{dove}
\usenavigationsymbolstemplate{}
\title{Research?}
\author{Pieter Brederode, Timo Koppenberg, \\ Jelco Bodewes, Anton Golov}
\institute{B3OMI}

@@

\section{Introduction}
\begin{frame}{Overview}
    \begin{itemize}
        \item We did research!
        \item That's it, really.
    \end{itemize}
\end{frame}

>>>>

\usetheme{Dresden}
\usecolortheme{dove}
\usenavigationsymbolstemplate{}
\title{Research?}
\author{Pieter Brederode, Jelco Bodewes, \\ Timo Koppenberg, Anton Golov}
\institute{B3OMI}

@@

\section{Introduction}
\begin{frame}{Overview}
    \begin{itemize}
        \item Problem Statement
        \item Measurement Implementation
        \item Results
        \item Conclusions
    \end{itemize}
\end{frame}

\begin{frame}{Context: Whitelist/Blacklist}
    \begin{itemize}
        \item Program that given a URL decides whether to allow access.
        \item Different possible granualities:
        \begin{itemize}
            \item IP address (32 bit integer)
            \item Domain name (20 char string)
            \item Full path (100 char string)
        \end{itemize}
        \item Fast insert and query
        \item Low memory usage
    \end{itemize}
\end{frame}

\begin{frame}{Implementation}
    \begin{itemize}
        \item C++
        \begin{itemize}
            \item We hoped for predictable performance\ldots
            \item Standard library has hash table and binary search tree
            \item Standard library has timing tools
        \end{itemize}
        \item Open source SkipList library (\texttt{CSSkipList})
        \begin{itemize}
            \item Weird results can be investigated directly
            \item Turned out useful
        \end{itemize}
        \item POSIX API for memory usage
    \end{itemize}
\end{frame}

\begin{frame}{Implementation Issues}
    \begin{itemize}
        \item POSIX API for memory is too coarse
        \begin{itemize}
            \item Added tracking of alloctions
            \item Bonus: only track the data structure itself
            \item Required modifying the SkipList
        \end{itemize}
        \item Performance is consistent, but unusual
        \begin{itemize}
            \item Hash tables are quirky
            \item Suspect: the allocator
            \item Run tests in separate process
            \begin{itemize}
                \item Or write your own allocator\ldots
            \end{itemize}
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Small hash tables are expensive}

\end{frame}

\begin{frame}{Big hash tables are cheap}

\end{frame}
